\documentclass{scrartcl}

\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage{hyperref} % Add a link to your document
\usepackage{graphicx} % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage[top=75px, bottom=75px, left=85px, right=85px]{geometry} % Change page borders
\usepackage{color}
%footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot[R]{Context Project: Gamygdala-Integration}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\title{Project Documentation}
\subtitle{Group: Gamygdala-Integration}
\date{\today{}}

\author{
    \begin{tabular}{l r}
      B.L.L. Kreynen\\
      M. Spanoghe\\
      R.A.N. Starre\\
      Yannick Verhoog\\
      Joost Wooning\\
    \end{tabular}
}

\maketitle \thispagestyle{empty} \pagebreak

\section{Guide}
Here we will list a guide to get the project (with our current implementations) working locally. Also we will explain how you can run a basic demo.

\subsection{download}
First you will need to download the repository from Github on this link: \\
\url{https://github.com/tygron-virtual-humans/Integration-runtime}\\
You can either download the zip (recommended for single use) or use the Github client to clone this repository locally (recommended when you want to receive any updates in the future).
Secondly you will need a IDE to work with. It is important that this IDE has a maven plug-in because the repository will need a lot of dependencies and maven can resolve all of this automatically when installed. Therefore we recommend Eclipse with maven:\\
\url{https://www.eclipse.org/downloads/packages/eclipse-ide-java-developers/lunasr2}
Finally you will need Java 7 to run the project. Make sure you have at least Java 7.

Thus, when you have installed eclipse and when you have the repository locally you can proceed.

\subsection{project}
Open Eclipse and right click to import a project. After you imported the repository you downloaded, you will need to right click on it and press "convert to maven project". Then, you have to right click again and press "maven install" under the maven tab.

\subsection{running the demo}
To run the demo look in the runtime project for a map called goal.demo.BW4TTest. Run the server jar by double clicking on it and then run the .java file by right clicking on it and press run as Java application.

\subsection{updates}
When we update our implementation this version is outdated. You can either download the repo again (now the latest version) and go back to step "project" or you can pull the updates when you use the Github client.
Note: Each time you download the new zip, you will need to re import the project in Eclipse.


\subsection{Questions}
If you have any questions about the project setup, feel free to leave an issue or question at our Github project page.


\end{document}