\documentclass{scrartcl}

\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage{hyperref} % Add a link to your document
\usepackage{graphicx} % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage[top=75px, bottom=75px, left=85px, right=85px]{geometry} % Change page borders
\usepackage{color}
%footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot[R]{Context Project: Gamygdala-Integration}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\title{Context Project: Virtual Human}
\subtitle{Group: Gamygdala-Integration}
\date{\today{}}

\author{
    \begin{tabular}{l r}
      B.L.L. Kreynen\\
      M. Spanoghe\\
      R.A.N. Starre\\
      Yannick Verhoog\\
      Joost Wooning\\
    \end{tabular}
}

\maketitle \thispagestyle{empty} \pagebreak

\section{Sprint reflection}

\subsection{Main Problems Encountered}

\emph{Problem 1}. We forgot to mention the written deliverables. For example, we didn't write down a specific task for the product plan. This was an extra task.\\
\emph{Reaction}. We managed to fill it in and deliver it on time.\\
\\
\emph{Problem 2}. Setting up TravisCI and Octopull wasn't ready on time because setting up the projects with maven caused a lot of unexpected problems. Together with the extra product plan task, we didn't have enough time to complete it.\\
\emph{Reaction}. We focused on setting up the repositories locally and get maven to work with it. We will add it to the backlog of next week.\\
\\
\emph{Problem 3}. For the tasks of week 3 two tasks had a lot of overlap and there for the division was a bit unclear. (Understand GOAL architecture/Looking for structural location to implement emotions)\\
\emph{Reaction}. One of the tasks is completed and the other one is only completed partially. The result is that we did finish this task, but that was a bit unclear for the responsible students.\\
\\
\emph{Problem 4}. Some tasks were not feasible yet because they involved other groups and they didn't have enough work done to help us or to show us their implementation yet.
\emph{Reaction}. We ignored these tasks and worked on other tasks. It will be added to the backlog for next week.\\
\\
\emph{Problem 5}. Because we did more research than actual coding we didn't had much to show as a demo at the end of the week. This was a problem because grading on the product was thus almost not feasible.
\emph{Reaction}. As a solution we took a part of the tasks planned for next week and implemented them as fast as possible.

\subsection{Adjustments for next sprint plan}
For the next sprint plans we will take a closer look at the coding deliverables but also at the written ones since we tend to forget to mention them in the backlog.
Also we will make sure that tasks don't overlap too much.
We should watch out for problem 4, but it is hard to know this in advance.
Finally we should really think about the product and about the demo in advance so that we implement the most important tasks first.
\end{document}